WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2019-03-02 paper/ms.tex
all referee changes added, ready for JNW review

\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
%\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{comment}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{\today}
\revised{---}
\accepted{---}
\submitjournal{AAS journals.}

@@

%\NewPageAfterKeywords
\listofchanges

@@

\added{

@@

}

@@

@@

\added{\author{M. Fausnaugh} % faus@mit.edu CONFIRMED

@@

02139, USA }}

@@

}

\begin{abstract}
    The Transiting Exoplanet Survey Satellite (TESS) recently observed
    18 transits of the hot Jupiter WASP-4b.  The sequence of transits
    occurred $81.6 \pm 11.7$~seconds earlier than had been predicted,
    based on data stretching back to 2007.  This is unlikely to be the
    result of a clock error, because TESS observations of other hot
    Jupiters (WASP-6b, 18b, and 46b) are compatible with a constant
    period, ruling out an 81.6-second offset at the 6.4$\sigma$ level.
    The 1.3-day orbital period of WASP-4b appears to be decreasing at
    a rate of $\dot{P} = -12.6 \pm 1.2$ milliseconds per year.  The
    apparent period change might be caused by tidal orbital decay or
    apsidal precession, although both interpretations have
    shortcomings.  The gravitational influence of a third body is
    another possibility, although at present there is \replaced{no}{minimal} 
    evidence for
    such a body. Further observations are needed to confirm and
    understand the timing variation.
\end{abstract}

@@

Although the Transiting Exoplanet Survey Satellite (TESS, \added{
\citealt{ricker_transiting_2015}}) is designed
to detect new planets, it is also performing precise photometric
monitoring of most of the planets that have been discovered by
ground-based transit surveys over the last two decades.  One of the
applications of the new TESS data is to search for timing anomalies in
hot Jupiter systems.  Long-term monitoring of hot Jupiter transit and
occultation times should eventually reveal two distinct processes.

First, whenever the orbital angular momentum is less than 3 times the
rotational angular momentum, the system is vulnerable to tidal orbital
decay \citep{counselman_outcomes_1973,hut_stability_1980}.  Most hot
Jupiters satisfy this condition and their orbits should be shrinking
\citep{levrard_falling_2009,matsumura_tidal_2010}.  The rate of decay,
which depends on how friction dissipates the energy of tidal
disturbances, is difficult to observe directly or calculate from first
principles. This has been a stubborn source of uncertainty in the
interpretation of many phenomena in stellar and planetary astrophysics
(as reviewed by \citealt{Mazeh2008} and \citealt{ogilvie_tidal_2014}).

Second, long-term timing studies may reveal apsidal precession, {\it
i.e.}, the rotation of the orbital ellipse within the orbital plane.
Apsidal precession has long been observed in eclipsing binaries
\citep[{\it e.g.},][]{
  schwarzschild_structure_1958,torres_accurate_2010,borkovits_eclipse_2015}.
For exoplanets, precessing orbits have been detected in a handful of
cases, including circumbinary systems (Kepler-413
\citealt{kostov_kepler-413b_2014}; Kepler-453
\citealt{welsh_kepler_2015}), planets orbiting rapidly rotating stars
(Kepler-13
\citealt{szabo_spin-orbit_2012,szabo_mapping_2014},~\citealt{masuda_spin-orbit_2015});
and systems with multiple interacting giant planets (Kepler-108
\citealt{mills_kepler-108_2017}; Kepler-693
\citealt{masuda_eccentric_2017}).  Apsidal precession is not regularly
observed in hot Jupiter systems because their orbits are nearly
circular, which may itself be a consequence of star-planet tides.  If
it could be observed, then as \citet{ragozzine_probing_2009} showed it
would be possible to measure the planet's Love number, which would be
a valuable constraint on the planet's interior.

So far, the most convincing direct evidence for either orbital decay
or apsidal precession has come from WASP-12b.
\citet{maciejewski_departure_2016} and \citet{patra_2017} showed that
the transit period of WASP-12b has been steadily decreasing by about
30~milliseconds per year over the last decade.  Here, we present
evidence for a timing anomaly in the WASP-4 system.  The hot Jupiter
WASP-4b orbits a G7V star every 1.34 days, corresponding to an orbital
distance of 5.5 stellar radii
\citep{wilson_wasp-4b_2008,huitson_gemini_2017}.  It is a good target
to search for departures from a constant period, because transit data
exist all the way back to 2007.  The orbital eccentricity is less than
0.018 (2$\sigma$), based on the work of \cite{knutson_friends_2014},
who combined the available transit times, occultation times, and
Doppler data.  The sky projection of the stellar obliquity
is also compatible with zero, within about 10 degrees
\citep{triaud_spin-orbit_2010,sanchis-ojeda_starspots_2011}.

In what follows, \S~\ref{sec:observations} presents the new TESS
observations, and \S~\ref{sec:timing} describes our timing analysis.
We tried fitting the data with three models: a constant period, a
decaying period, and a slightly eccentric precessing orbit.  A
constant period can be ruled out, but we cannot distinguish between
the latter two possibilities.  Either possibility would have
interesting implications, described in \S~\ref{sec:implications}.
Appendix~\ref{sec:verify_tess} considers the possibility that the
WASP-4 timing anomaly is due to an error in timestamps in the TESS
data products.  We found this possibility to be unlikely because none
of the other hot Jupiters we examined show a timing offset with the
same amplitude as was seen for WASP-4.

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=0.9\textwidth]{f2.png}
    \end{center}
    \vspace{-0.7cm}
    \caption{
        {\bf Phase-folded lightcurve of WASP-4b.} Gray points are
        TESS \replaced{data}{flux measurements, with median 
        $1\sigma$ error shown in the lower 
        right.} 
        Yellow points are binned measurements.  The bottom
        panel shows the residuals.  The fit to the phase-folded
        transit (blue line) is used when measuring mid-transit times
        \replaced{for the}{of} individual transits (see 
        \S~\ref{sec:measurement}).
        \label{fig:phasefold}
    }
\end{figure*}

@@

We began our analysis with the Presearch Data Conditioning (PDC)
lightcurve\replaced{ 
\citep{smith_kepler_apertures_2017,smith_kepler_PDC_2017}}{, which has had 
systematic trends removed 
through the decorrelation process described by 
\citet{smith_kepler_apertures_2017,smith_kepler_PDC_2017}}.
We \added{then} processed the lightcurve as follows.  First, we removed all 
points
with non-zero quality flags.  This removed data that might have been
adversely affected by ``momentum dumps,'' the firing of thrusters and
resetting of reaction
wheels\footnote{\added{Details concerning the spacecraft pointing and momentum 
dumps are described in the data release 
notes:}\url{archive.stsci.edu/missions/tess/doc/tess_drn/tess_sector_02_drn02_v01.pdf}}
that took place every 2.5 days during sector 2
\deleted{\citep{tess_data_product_description_2018}}.  The data during these
events were assigned quality flags corresponding to ``Reaction Wheel
Desaturation Event'' and ``Manual Exclude'' 
\added{\citep[][Table 28]{tess_data_product_description_2018}}.  For WASP-4, 
these flags
were simultaneously set for 54 distinct cadences, and there were 10
momentum dumps, averaging about 10 minutes of flagged data per dump.
Out of caution, we clipped out an additional 10 minutes before and
after every momentum dump.  We also removed the data within the first
and last hours of both orbits, because of \replaced{ramp-like systematic 
effects that appear}{correlated red noise that appears} during those time 
ranges.

@@

To verify that the measured uncertainties are estimated accurately, we
computed the \deleted{reduced} $\chi^2$ \added{value} for a linear ephemeris 
fit to the
measured TESS mid-transit times.  We found that $\chi^2 = 9.2$, with
$n=16$ degrees of freedom.  The variance of the $\chi^2$ distribution
is $2n$, so we would expect $\chi^2 = 16 \pm 5.7$.  Visually
inspecting the residuals showed that the error variance had been
overestimated, so we multiplied the measured TESS errors by a factor
$f=0.76$, forcing a reduced $\chi^2$ of unity.  This lowered the mean
uncertainty of the transit midtimes from $29.8$ to $22.6$ seconds.  We
verified that omitting this step did not appreciably alter any of our
conclusions.

@@

\startdata
{\it Transit/RV parameters:} & & & \\
  $R_{\rm p}/R_\star$                        & $0.15201$              & $+0.00040$, $-0.00033$      & A \\
  $i$~[deg]                                  & $89.06$                & $+0.65$, $-0.84$            & A \\
  $a/R_\star$                                & $5.451$                & $+0.023$, $-0.052$          & A \\
  $u_{\rm linear}$                           & $0.382$                & ---                         & A \\
  $u_{\rm quad}$                             & $0.210$                & ---                         & A \\
  $K$~[m~s$^{-1}$]                           & $241.1$                & $+2.8$, $-3.1$              & B \\
{\it Stellar parameters:} & & & \\
  $T_{\rm eff}$~[K]                          & $5400$                 & $\pm 90$                    & C \\
  $\log g_\star$~[cgs]                       & $4.47$                 & $\pm 0.11$                  & C \\
  $[{\rm Fe/H}]$                             & $-0.07$                & $\pm 0.19$                  & C \\
  $F_{\rm bol}$~[erg~cm$^{-2}$~s$^{-1}$]     & $2.802\times10^{-10}$  & $\pm 0.076\times10^{-10}$   & D \\
  $A_V$~[mag]                                & $0.03$                 & $+0.02, -0.01$              & D \\
  $\pi$~[mas]                                & $3.7145$               & $0.0517$                    & F \\
  $R_\star$~[R$_{\odot}$]                    & $0.893$                & $\pm 0.034$                 & E \\
  $\rho_\star$~[g~cm$^{-3}$]                 & $1.711$                & $+0.022$, $-0.048$          & E \\
  $M_\star$~[M$_{\odot}$]                    & $0.864$                & $+0.084$, $-0.090$          & E \\
  $T$ magnitude                              & $11.778$               & $\pm 0.018$                 & G \\
  %Rotation period~[days]                     & $\approx$34            & ---                         & H \\
{\it Planetary parameters:} & & & \\
  $a$~[AU]                                   & $0.0226$               & $+0.0007$, $-0.0008$        & E \\
  $M_p$~[M$_{\rm Jup}$]                      & $1.186$                & $+0.090$, $-0.098$          & E \\
  $R_p$~[R$_{\rm Jup}$]                      & $1.321$                & $\pm 0.039$                 & E \\
\enddata

\tablecomments{
  (A) From phase-folded TESS lightcurve (\S~\ref{sec:measurement}).
  Orbital periods are in Table~4. The limb darkening parameters were
  allowed to float around the \citet{claret_limb_2017} prediction, but
  were unconstrained.
  (B) \citet{triaud_spin-orbit_2010}.
  (C) From HARPS spectra \citep{doyle_accurate_2013}.
  (D) \citet{stassun_accurate_2017}.
  (E) This work, see \S~\ref{sec:system_parameters}.
  (F) \citet{gaia_collaboration_gaia_2018}.
  (G) \citet{stassun_TIC_2018}.
  %(H) \citet{hoyer_tramos_2013}, from star-spot occultation events.
}

@@

Table~1 gives the resulting parameters, which we adopted for the
remaining analysis.
\added{The uncertainties in our derived stellar and planetary parameters
    are propagated according to standard analytic formulae, under the 
    assumption of uncorrelated and normally distributed initial measurements.}
Our \added{system} parameters are in agreement with those of
previous investigators, but have the benefit of incorporating the {\it
Gaia} parallax
\citep{wilson_wasp-4b_2008,gillon_discovery_2009,winn_transit_2009,southworth_homogeneous_2011,petrucci_no_2013,huitson_gemini_2017}.
By comparing the star's luminosity and spectroscopic parameters with
the outputs of the Yonsei-Yale stellar-evolutionary models, we found
that WASP-4 is a main-sequence star with an age of approximately
$7\,{\rm Gyr}$ \added{\citep{demarque_y2_2004}}.

@@

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.49\textwidth]{f3.pdf}
    \end{center}
    \vspace{-0.6cm}
    \caption{ {\bf TESS saw WASP-4b transit earlier than expected.}
      Both plots show the deviations between the observed and
      calculated transit times, where the calculation is based only on
      \deleted{the} pre-TESS data and assumes a constant period.  The blue 
      bands
      depict the $\pm$$1\sigma$ credible interval of the predicted
      times.  {\it Top:} The full timing dataset spans 11 years. The
      darkest points correspond to the most precise data. \added{The binned 
      TESS point is the weighted average of 18 TESS transits.}  {\it
        Bottom:} Close-up of the TESS observations. The red band shows
      the average deviation of the TESS transits \added{($\pm 1\sigma$)}, 
      which arrived $81.6 \pm 11.7\ {\rm seconds}$ earlier than predicted.
        \label{fig:arrived_early}
    }
\end{figure}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Timing residuals and best-fit models for WASP-4b.}
		\replaced{The residuals are the observed times minus the calculated 
		times assuming a constant period. The darkest points correspond to
        the most precise data.}{The vertical axis shows the 
		observed times minus the calculated times assuming a constant period 
		for transits ({\it top}) and occultations ({\it bottom}). Darker 
		points correspond to more precise data.}
        The constant-period model (gray line) is
		a poor description of the data.  Models with a uniformly
		decreasing period (blue) or apsidal precession (orange) provide
		better fits\deleted{ to the data}.  The red square represents the
		combination of all the TESS data and is for display purposes
		only.  The models were fitted to all of the individual transit
		times.
		\label{fig:times}
	}
\end{figure*}

@@

First, we \replaced{fitted}{performed a weighted least-squares fit of} a 
constant-period model (\added{a} ``linear ephemeris'') to the
pre-TESS data, and used it to extrapolate to the epochs of the TESS
observations.  The residuals of the best fitting model are shown in
Figure~\ref{fig:arrived_early}.  The transits observed by TESS
occurred earlier than expected.  Because the TESS mission is still in
an early stage, we were concerned about a possible offset in the TESS
timestamps due to an error with the TESS clock or the data processing
pipeline.  Appendix~\ref{sec:verify_tess} describes some tests that
convinced us that a simple offset is unlikely. Assuming that the
observed timing variation is astrophysical, we proceeded by exploring
three models for the timing data in a manner identical to the study
by~\citet{patra_2017}.

@@

\added{We fit each model by assuming a Gaussian likelihood and sampling over 
the posterior probability distributions. The prior for the quadratic
model allowed the period derivative to have any sign.}
Figure~\ref{fig:times} shows the residuals with respect to the
constant-period model.  The best-fitting constant-period model has
$\chi^2 = 174$ and 61 degrees of freedom.  The best-fitting
\replaced{decreasing-period}{quadratic} model has $\chi^2 = 62.6$ and 60 degrees of freedom.
The best-fitting precession model has $\chi^2 = 64.3$ and 58 degrees
of freedom.  Either of the latter two models provides a much better
fit than the constant-period model.  The difference in $\chi^2$
between the first and second models corresponds to $p \approx
10^{-26}$.

@@

In the \replaced{decreasing-period}{quadratic} model, the period derivative is
\begin{equation}
\dot{P}
  = - (4.00 \pm 0.38)\times 10^{-10}
  = - 12.6 \pm 1.2~{\rm ms}\,{\rm yr}^{-1}.
  \label{eq:dP_dt_obs}
\end{equation}
For comparison, the best-fitting period derivative of WASP-12b is
$\dot{P} = -29 \pm 3\,{\rm ms}\,{\rm yr}^{-1}$
\citep{maciejewski_departure_2016,patra_2017}.  If both planets are
truly falling onto their stars, then WASP-4b is falling at about half
the rate of WASP-12b.  In the precession model, the best-fit
eccentricity is
\begin{equation}
  e = (1.92^{+ 1.93}_{- 0.76})\times10^{-3}
  \label{eq:e_obs}
\end{equation}
The longitude of periastron advances by $\dot{\omega} =
13.6^{+4.7}_{-3.6}\ {\rm degrees}\,{\rm yr}^{-1}$, and the precession
period is $27^{+10}_{-7}$ years.  All of the best-fitting parameters
(the medians of the posterior distributions) and the 68\% credible
intervals are reported in Table~4.

\added{
To assess the robustness of these results, we considered a few
possible systematic effects in the timing dataset.  One concern in the
pre-TESS timing measurements was incomplete phase coverage: a handful
of the transit times in Table~2 are from lightcurves with partial
gaps.  A separate issue is the effect of spot-crossing anomalies on
mid-transit time measurements.  Both effects lead to lightcurve
asymmetries which skew transit-time measurements.

>>>>

\documentclass[12pt,twocolumn,tighten]{aastex62}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
%\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{December 22, 2018}
\revised{\today}
\accepted{---}
\submitjournal{AAS journals.}

@@

\NewPageAfterKeywords
\listofchanges

@@

@@

@@

\altaffiliation{ Kavli Fellow }

@@

\author{M. Fausnaugh} % faus@mit.edu CONFIRMED

@@

@@

\begin{abstract}
    The Transiting Exoplanet Survey Satellite (TESS) recently observed
    18 transits of the hot Jupiter WASP-4b.  The sequence of transits
    occurred $81.6 \pm 11.7$~seconds earlier than had been predicted,
    based on data stretching back to 2007.  This is unlikely to be the
    result of a clock error, because TESS observations of other hot
    Jupiters (WASP-6b, 18b, and 46b) are compatible with a constant
    period, ruling out an 81.6-second offset at the 6.4$\sigma$ level.
    The 1.3-day orbital period of WASP-4b appears to be decreasing at
    a rate of $\dot{P} = -12.6 \pm 1.2$ milliseconds per year.  The
    apparent period change might be caused by tidal orbital decay or
    apsidal precession, although both interpretations have
    shortcomings.  The gravitational influence of a third body is
    another possibility, though at present there is
    \replaced{no}{minimal} evidence for such a body. Further
    observations are needed to confirm and understand the timing
    variation.
\end{abstract}

@@

Although the Transiting Exoplanet Survey Satellite (TESS\added{,
\citealt{ricker_transiting_2015}}) is designed to detect new planets,
it is also \replaced{performing precise photometric monitoring
of}{precisely monitoring} most of the planets that have been
discovered by ground-based transit surveys over the last two decades.
One \replaced{of the applications}{application} of the new TESS data
is to search for timing anomalies in \added{previously known }hot
Jupiter systems.  Long-term monitoring of hot Jupiter transit and
occultation times should eventually reveal \replaced{two
distinct}{three select} processes.

\explain{The following four paragraphs have been modified to add
emphasis to the possibility of an outer planet explaining the timing
deviations. Some background information given in the original
submission has been removed.}

First, the orbits of most hot Jupiters should shrink because of tidal
orbital decay
\citep{counselman_outcomes_1973,hut_stability_1980,levrard_falling_2009,matsumura_tidal_2010}.
Directly measuring the rate of decay might lead to an improved
understanding of how friction dissipates the energy of tidal
disturbances (a problem reviewed by \citealt{Mazeh2008} and
\citealt{ogilvie_tidal_2014}).

Second, if hot Jupiter orbits are at all eccentric, then long-term
timing studies should reveal rotation of the orbital ellipse within
the orbital plane (``apsidal precession'').  If this effect were
observed, it could yield a measure of the planet's Love number, which
would constrain the planet's interior structure
\citep{ragozzine_probing_2009}.

The most convincing direct evidence yet found for either orbital decay
or apsidal precession of a hot Jupiter is the case of WASP-12b, which
has a transit period that has decreased by about 30~milliseconds per
year over the last decade
\citep{maciejewski_departure_2016,patra_2017}.

The final effect of interest that can produce period changes in hot
Jupiter systems is gravitational acceleration caused by massive outer
companions \citep[{\it e.g.},][Section~4]{agol_detecting_2005}.
Prototypes include WASP-53 and WASP-81, systems in which the inner hot
Jupiters are periodically perturbed by eccentric brown dwarf
companions with semimajor axes of a few astronomical units
\citep{triaud_peculiar_2017}.

% DELETED THE FOLLOWING TEXT FROM SUBMITTED VERSION:
% First, whenever the orbital angular momentum is less than 3 times
% the rotational angular momentum, the system is vulnerable to tidal
% orbital decay \citep{counselman_outcomes_1973,hut_stability_1980}.
% Most hot Jupiters satisfy this condition and their orbits should be
% shrinking \citep{levrard_falling_2009,matsumura_tidal_2010}.  The
% rate of decay, which depends on how friction dissipates the energy
% of tidal disturbances, is difficult to observe directly or calculate
% from first principles. This has been a stubborn source of
% uncertainty in the interpretation of many phenomena in stellar and
% planetary astrophysics (as reviewed by \citealt{Mazeh2008} and
% \citealt{ogilvie_tidal_2014}).
%
% Second, long-term timing studies may reveal apsidal precession, {\it
% i.e.}, the rotation of the orbital ellipse within the orbital plane.
% Apsidal precession has long been observed in eclipsing binaries
% \citep[{\it
% e.g.},][]{schwarzschild_structure_1958,torres_accurate_2010,borkovits_eclipse_2015}.
% For exoplanets, precessing orbits have been detected in a handful of
% cases, including circumbinary systems (Kepler-413
% \citealt{kostov_kepler-413b_2014}; Kepler-453
% \citealt{welsh_kepler_2015}), planets orbiting rapidly rotating
% stars (Kepler-13
% \citealt{szabo_spin-orbit_2012,szabo_mapping_2014},~\citealt{masuda_spin-orbit_2015});
% and systems with multiple interacting giant planets (Kepler-108
% \citealt{mills_kepler-108_2017}; Kepler-693
% \citealt{masuda_eccentric_2017}).  Apsidal precession is not
% regularly observed in hot Jupiter systems because their orbits are
% nearly circular, which may itself be a consequence of star-planet
% tides.  If it could be observed, then as
% \citet{ragozzine_probing_2009} showed it would be possible to
% measure the planet's Love number, which would be a valuable
% constraint on the planet's interior.
%
% So far, the most convincing direct evidence for either orbital decay
% or apsidal precession has come from WASP-12b.
% \citet{maciejewski_departure_2016} and \citet{patra_2017} showed
% that the transit period of WASP-12b has been steadily decreasing by
% about 30~milliseconds per year over the last decade.

Here, we present evidence for a timing anomaly in the WASP-4 system.
The hot Jupiter WASP-4b orbits a G7V star every 1.34 days,
corresponding to an orbital distance of 5.5 stellar radii
\citep{wilson_wasp-4b_2008,huitson_gemini_2017}.  It is a good target
to search for departures from a constant period, because transit data
exist all the way back to 2007.  The orbital eccentricity is less than
0.018 (2$\sigma$), based on the work of \cite{knutson_friends_2014},
who combined the available transit times, occultation times, and
Doppler data.  The sky projection of the stellar obliquity is also
compatible with zero, within about 10 degrees
\citep{triaud_spin-orbit_2010,sanchis-ojeda_starspots_2011}.

In what follows, \S~\ref{sec:observations} presents the new TESS
observations, and \S~\ref{sec:timing} describes our timing analysis.
We tried fitting the data with three models: a constant period, a
decaying period, and a slightly eccentric precessing orbit.  A
constant period can be ruled out\replaced{, but we}{. We} cannot
distinguish between the \replaced{latter two possibilities}{
  possibilities of a decaying orbit, a precessing orbit, and the
  unmodeled possibility of an orbit being gravitationally perturbed by
  an outer companion}.  \replaced{Either possibility}{Any of the three
scenarios} would have interesting implications\replaced{, described in
\S~\ref{sec:implications}}{ (\S~\ref{sec:implications}), and more data
are required for a definitive ruling (\S~\ref{sec:future}).}
Appendix~\ref{sec:verify_tess} considers the possibility that the
WASP-4 timing anomaly is due to an error in timestamps in the TESS
data products.  We found this possibility to be unlikely because none
of the other hot Jupiters we examined show a timing offset with the
same amplitude as was seen for WASP-4.

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=0.9\textwidth]{f2.png}
    \end{center}
    \vspace{-0.7cm}
    \caption{
        {\bf Phase-folded lightcurve of WASP-4b.} Gray points are
        TESS \replaced{data}{flux measurements, with median 
        $1\sigma$ uncertainty shown in the lower 
        right.} 
        Yellow points are binned measurements.  The bottom
        panel shows the residuals.  The fit to the phase-folded
        transit (blue line) is used when measuring mid-transit times
        \replaced{for the}{of} individual transits (see 
        \S~\ref{sec:measurement}).
        \label{fig:phasefold}
    }
\end{figure*}

@@

We began our analysis with the Presearch Data Conditioning (PDC)
lightcurve\replaced{
  \citep{smith_kepler_apertures_2017,smith_kepler_PDC_2017}}{, which
has had non-astrophysical variability removed through the methods
discussed by \citet{smith_kepler_apertures_2017} and
\citet{smith_kepler_PDC_2017}}.  We \added{then} processed the
lightcurve as follows.  First, we removed all points with non-zero
quality flags.  This removed data that might have been adversely
affected by ``momentum dumps,'' the firing of thrusters and resetting
of reaction wheels\footnote{\added{The spacecraft pointing and
momentum dumps are described in the data release notes:
}\url{archive.stsci.edu/missions/tess/doc/tess_drn/tess_sector_02_drn02_v01.pdf}}
that took place every 2.5 days during sector 2\deleted{
  \citep{tess_data_product_description_2018}}.  The data during these
events were assigned quality flags corresponding to ``Reaction Wheel
Desaturation Event'' and ``Manual Exclude'' \added{\citep[][Table
28]{tess_data_product_description_2018}}.  For WASP-4, these flags
were simultaneously set for 54 distinct cadences, and there were 10
momentum dumps, averaging about 10 minutes of flagged data per dump.
Out of caution, we clipped out an additional 10 minutes before and
after every momentum dump.  We also removed the data within the first
and last hours of both orbits, because of \replaced{ramp-like
systematic effects that appear}{correlated red noise that appears}
during those time ranges.

@@

To verify that the measured uncertainties are estimated accurately, we
computed the \deleted{reduced }$\chi^2$\added{ value} for a linear
ephemeris fit to the measured TESS mid-transit times.  We found that
$\chi^2 = 9.2$, with $n=16$ degrees of freedom.  The variance of the
$\chi^2$ distribution is $2n$, so we would expect $\chi^2 = 16 \pm
5.7$.  Visually inspecting the residuals showed that the error
variance had been overestimated, so we multiplied the measured TESS
errors by a factor $f=0.76$, forcing a reduced $\chi^2$ of unity.
This lowered the mean uncertainty of the transit midtimes from $29.8$
to $22.6$ seconds.  We verified that omitting this step did not
appreciably alter any of our conclusions.

@@

\startdata
{\it Transit/RV parameters:} & & & \\
  $R_{\rm p}/R_\star$                        & $0.15201$              & $+0.00040$, $-0.00033$      & A \\
  $i$~[deg]                                  & $89.06$                & $+0.65$, $-0.84$            & A \\
  $a/R_\star$                                & $5.451$                & $+0.023$, $-0.052$          & A \\
  $u_{\rm linear}$                           & $0.382$                & ---                         & A \\
  $u_{\rm quad}$                             & $0.210$                & ---                         & A \\
  $K$~[m~s$^{-1}$]                           & $241.1$                & $+2.8$, $-3.1$              & B \\
{\it Stellar parameters:} & & & \\
  $T_{\rm eff}$~[K]                          & $5400$                 & $\pm 90$                    & C \\
  $\log g_\star$~[cgs]                       & $4.47$                 & $\pm 0.11$                  & C \\
  $[{\rm Fe/H}]$                             & $-0.07$                & $\pm 0.19$                  & C \\
  $F_{\rm bol}$~[erg~cm$^{-2}$~s$^{-1}$]     & $2.802\times10^{-10}$  & $\pm 0.076\times10^{-10}$   & D \\
  $A_V$~[mag]                                & $0.03$                 & $+0.02, -0.01$              & D \\
  $\pi$~[mas]                                & $3.7145$               & $0.0517$                    & F \\
  $R_\star$~[R$_{\odot}$]                    & $0.893$                & $\pm 0.034$                 & E \\
  $\rho_\star$~[g~cm$^{-3}$]                 & $1.711$                & $+0.022$, $-0.048$          & E \\
  $M_\star$~[M$_{\odot}$]                    & $0.864$                & $+0.084$, $-0.090$          & E \\
  $T$ magnitude                              & $11.778$               & $\pm 0.018$                 & G \\
{\it Planetary parameters:} & & & \\
  $a$~[AU]                                   & $0.0226$               & $+0.0007$, $-0.0008$        & E \\
  $M_p$~[M$_{\rm Jup}$]                      & $1.186$                & $+0.090$, $-0.098$          & E \\
  $R_p$~[R$_{\rm Jup}$]                      & $1.321$                & $\pm 0.039$                 & E \\
\enddata

\tablecomments{
  (A) From phase-folded TESS lightcurve (\S~\ref{sec:measurement}).
  Orbital periods are in Table~4. The limb darkening parameters were
  allowed to float around the \citet{claret_limb_2017} prediction, but
  were unconstrained.
  (B) \citet{triaud_spin-orbit_2010}.
  (C) From HARPS spectra \citep{doyle_accurate_2013}.
  (D) \citet{stassun_accurate_2017}.
  (E) This work, see \S~\ref{sec:system_parameters}.
  (F) \citet{gaia_collaboration_gaia_2018}.
  (G) \citet{stassun_TIC_2018}.
}

@@

Table~1 gives the resulting parameters, which we adopted for the
remaining analysis.  \added{The uncertainties in our derived stellar
and planetary parameters are propagated according to standard analytic
formulae, under the assumption that the variables are uncorrelated and
normally distributed.} Our \added{system} parameters are in agreement
with those of previous investigators, but have the benefit of
incorporating the {\it Gaia} parallax
\citep{wilson_wasp-4b_2008,gillon_discovery_2009,winn_transit_2009,southworth_homogeneous_2011,petrucci_no_2013,huitson_gemini_2017}.
By comparing the star's luminosity and spectroscopic parameters with
the outputs of the Yonsei-Yale stellar-evolutionary models, we found
that WASP-4 is a main-sequence star with an age of approximately
$7\,{\rm Gyr}$ \added{\citep{demarque_y2_2004}}.

@@

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.49\textwidth]{f3.pdf}
    \end{center}
    \vspace{-0.6cm}
    \caption{ {\bf TESS saw WASP-4b transit earlier than expected.}
      Both plots show the deviations between observed and calculated
      transit times, where the calculation is based only on
      \deleted{the} pre-TESS data and assumes a constant period.  The
      blue bands depict the $\pm$$1\sigma$ credible interval of the
      predicted times.  {\it Top:} The full timing dataset spans 11
      years. The darkest points correspond to the most precise data.
      \added{The binned TESS point is the weighted average of 18 TESS
      transits.}  {\it Bottom:} Close-up of the TESS observations. The
      red band shows the average deviation of the TESS transits
      \added{($\pm 1\sigma$)}, which arrived $81.6 \pm 11.7\ {\rm
      seconds}$ earlier than predicted.
      \label{fig:arrived_early}
    }
\end{figure}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf Timing residuals and best-fit models for WASP-4b.}
  \replaced{The residuals are the observed times minus the calculated
  times assuming a constant period. The darkest points correspond to
  the most precise data.}{The vertical axis shows the observed times
  minus the calculated times assuming a constant period for transits
  ({\it top}) and occultations ({\it bottom}). Darker points
  correspond to more precise data.} The constant-period model (gray
  line) is a poor description of the data.  Models with a uniformly
  decreasing period (blue) or an eccentric, precessing orbit (orange)
  provide	better fits\deleted{ to the data}.  The red square
  represents the combination of all the TESS data and is for display
  purposes only.  The models were fitted to all of the individual
  transit times.
  \label{fig:times}
	}
\end{figure*}

@@

First, we \replaced{fitted}{performed a weighted least-squares fit of}
a constant-period model (\added{a }``linear ephemeris'') to the
pre-TESS data, and used it to extrapolate to the epochs of the TESS
observations.  The residuals of the best fitting model are shown in
Figure~\ref{fig:arrived_early}.  The transits observed by TESS
occurred earlier than expected.  Because the TESS mission is still in
an early stage, we were concerned about a possible offset in the TESS
timestamps due to an error with the TESS clock or the data processing
pipeline.  Appendix~\ref{sec:verify_tess} describes some tests that
convinced us that a simple offset is unlikely. Assuming that the
observed timing variation is astrophysical, we proceeded by exploring
three models for the timing data in a manner identical to the study
by~\citet{patra_2017}.

@@

\added{We fitted each model by assuming a Gaussian likelihood and
sampling over the posterior probability distributions. The prior for
the quadratic model allowed the period derivative to have any sign.}
Figure~\ref{fig:times} shows the residuals with respect to the
constant-period model.  The best-fitting constant-period model has
$\chi^2 = 174$ and 61 degrees of freedom.  The best-fitting
\replaced{decreasing-period}{quadratic} model has $\chi^2 = 62.6$ and
60 degrees of freedom.  The best-fitting precession model has $\chi^2
= 64.3$ and 58 degrees of freedom.  Either of the latter two models
provides a much better fit than the constant-period model.  The
difference in $\chi^2$ between the first and second models corresponds
to $p \approx 10^{-26}$.

@@

In the \replaced{decreasing-period}{quadratic} model, the period
derivative is
\begin{equation}
\dot{P}
  = - (4.00 \pm 0.38)\times 10^{-10}
  = - 12.6 \pm 1.2~{\rm ms}\,{\rm yr}^{-1}.
  \label{eq:dP_dt_obs}
\end{equation}
For comparison, the best-fitting period derivative of WASP-12b is
$\dot{P} = -29 \pm 3\,{\rm ms}\,{\rm yr}^{-1}$
\citep{maciejewski_departure_2016,patra_2017}.  If both planets are
truly falling onto their stars, then WASP-4b is falling at about half
the rate of WASP-12b.

In the precession model, the best-fit eccentricity is
\begin{equation}
  e = (1.92^{+ 1.93}_{- 0.76})\times10^{-3}
  \label{eq:e_obs}
\end{equation}
The longitude of periastron advances by $\dot{\omega} =
13.6^{+4.7}_{-3.6}\ {\rm degrees}\,{\rm yr}^{-1}$, and the precession
period is $27^{+10}_{-7}$ years.  All of the best-fitting parameters
(the medians of the posterior distributions) and the 68\% credible
intervals are reported in Table~4.

\explain{The following subsection has been added since the original
submission, per the referee's suggestions.}
\subsection{Systematic concerns}
